---
title: "linear model from Web"
author: "Diana Flores "
date: "summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

#introduction 
We predict a simulated strength score base on arm and grip strength. we will fined 3 models and compare them.
The response variable is numerical and the explanatory variable is numerical,so we use the num~num helper file. 


## Model 1 SIM~ARMS


## results

### graphical results
```{r}
model.1 <- lm(SIMS~ARM,data=data)
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```

As the arm strength increases sims increases.

### numerical results

```{r}
cor(SIMS~ARM,data=data)
```
The correlation is 0.69 which shows that arm strength is related to sim score

### inferentail results 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
We reject the null hypothesis ,because the intercept and the coefficient of ARM strength are significantly different from 0.

### prediction interval
```{r}
newdata = data.frame( ARM = 88 , GRIP=94)
predict(model.1, newdata, interval="predict")
```



The 95% prediction interval is from -1.7 to 3.1 for SIM score.


## Model 2 SIM~GRIP



### graphical results
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
plot(SIMS~GRIP,data=data)
abline(model.2, col='red')
```

As the grip strength increases the sims increases. The spread of the points around the regression line in the grip plot are more spread out than the arm strength plot.


### Numerical results 


```{r}
cor(SIMS~GRIP,data=data)
```
 The correlation is 0.63 which shows that grip plot is related to sim score.




### Inferential Results (Build model.2)


```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```



  

#### prediction intervol 

```{r}
newdata = data.frame( ARM = 88 , GRIP=94)
predict(model.2, newdata, interval="predict")
```


The prediction interval is from 0.15


#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP



### GRAPHICAL RESULTS 
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
print(summary(model.3))
```

As arm plus grip strength goes up, the simulation indicates that the sims goes up.


### Numerical results 


```{r}
cor(SIMS~ARM+GRIP,data=data)
```
The correlation is 0.73 which shows that arm strength is related to sims score.
  
### Inferential  RESULTS (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

Both the intercept and the coefficient ARM and GRIP strength are significant different from 0

  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

```{r}
anova(model.3,model.1)
```
The p value is .00000499 so i reject the null hypothesis. model 1 is better than model two becasue rss for model 1 is smaller.





```{r}
anova(model.3,model.2)
```


The model 3 is smaller then model 2 because the rss for model 3 is smaller.


# discussion and conclusion


In regards to the original question comparing both arm and grip strength to determine which is the best.Model 3 is the best because it has a smaller rss.
than model one and model two.









